Data Processing (Julia)

### 2025-05-02 notebooks/21_model.qmd
feat: juno dist with real solar wind data

```{julia}
using DrWatson: datadir
using CSV
using DataFrames, DataFramesMeta
using Unitful
using SpaceDataModel: parse_doy_datetime

"""Reads the solar wind parameters CSV file and returns a DataFrame."""
function read_sw_params_csv(file=datadir("jgra54158-sup-0001-supinfo.csv"))
    df = CSV.read(file, DataFrame)
    @chain df begin
        @transform! @byrow begin
            :time = parse_doy_datetime(:UTC)
            :N_PROTONS_CC = :N_PROTONS_CC * u"cm^-3"
            :V_KMPS = :V_KMPS * u"km/s"
        end
    end
    return df
end

>>>>

```{julia}
using DrWatson: datadir
using DataFrames, DataFramesMeta
using Unitful
using Juno.Data: read_sw_params_csv

### 2025-05-02 notebooks/30_data.qmd
feat: juno dist with real solar wind data

n, V, T, r = get_state_data()
b = get_mag_data()
```

@@

ds = ids_finder(b, period, V, n)

ds.r = r[Ti(Near(ds.time))]

df = dropmissing(ds)
```

@@

struct FitProduct{F,P} <: Function
    f::F
    param::P
    t_fit::DateTime
end

function (p::FitProduct)(t0, t1)
    tspan = DateTime(t0):Millisecond(10):DateTime(t1)
    xspan = (tspan .- p.t_fit) / Millisecond(1)
    data = p.f.(xspan, Ref(p.param))
    return DimVector(data, Ti(tspan))
end

@@

struct MVAProduct <: Function
    V
    B
    B_tspan
end

(p::MVAProduct)(t0, t1) = mva(p.V(t0, t1), p.B(p.B_tspan...))

@@

```{julia}
# 740, 1508, 4004, 4805
for i in [740, 1508, 4805]
    display(plot_candidate(df, i))
end
```

```{julia}
using Discontinuity: var_mapping

M = var_mapping(; j=:J_m_max_mva)
maps1 = [M.l_log M.l_norm_log; M.j_log M.j_norm_log]
maps2 = [M.density_log M.B_log; M.beta M.bm0_log];
df
begin
    color = r_map
    fnames = ["juno_distribution_r", "juno_sw_paramters"]
    # df = subset_by_quantiles(ds, [:L_n_cross, :j0_k, :j0_k_norm])
    df = dropmissing(ds)
    spec = data(df) * mapping(; color)
    fs = map([maps1, maps2]) do m
        plot_dist(spec, m;
            datalimits=datalimits_f,
            axis,
            figure
        )
    end
    resize_to_layout!.(fs)
    # easy_save.(fnames, fs)
    display.(fs)
end
```

>>>>

n, V, T, r = get_state_data()
jno_sw_params = read_sw_params_csv()
```

@@

ds = mapreduce(vcat, 2011:2016) do year
    b = get_mag_data(year)
    ids_finder(b, period, V, n)
end
```

```{julia}
using FlexiJoins
using StaticArrays
ds.r = r[Ti(Near(ds.time))]
ds.T = T[Ti(Near(ds.time))] * u"K"

df = dropmissing(ds)

df_sw = innerjoin(
    (ds, jno_sw_params),
    by_pred(x -> x.time .. (x.time + Minute(1)), ∋, :time);
)
@transform! df_sw @byrow begin
    :n = :N_PROTONS_CC
    :V = SA[:V_KMPS, 0, 0] * u"km/s"
    :T = :T_PROTONS_EV * u"eV"
    :r = "5 (Data)"
end
```

@@

struct FitProduct{F,P} <: Function
    f::F
    param::P
    t0::DateTime
end

function (p::FitProduct)(t0, t1)
    tspan = DateTime(t0):Millisecond(10):DateTime(t1)
    xspan = @. (tspan - p.t0) / Millisecond(1)
    data = p.f.(xspan, Ref(p.param))
    return DimVector(data, Ti(tspan))
end

@@

struct MVAProduct <: Function
    V
    B
    mva_tspan
end

(p::MVAProduct)(t0, t1) = mva(p.V(t0, t1), p.B(p.mva_tspan...))

@@

```{julia}
indices = eachindex(df.grad)[isnan.(df.grad)]
```

```{julia}
# 740, 1508, 4004, 4805
# 3094
for i in [4805]
    display(plot_candidate(df, i))
end
```

```{julia}
using Discontinuity: var_mapping, compute_params!

M = var_mapping(; log_str="", j=:J_m_max_mva, n=:n, B=:B_mag)
maps1 = [M.l_log M.l_norm_log; M.j_log M.j_norm_log]
maps2 = [M.density_log M.B_log; M.beta :V_mag];
let df = vcat(df, df_sw, cols=:intersect)
    color = r_map
    fnames = ["juno_distribution_r", "juno_sw_paramters"]
    # df = subset_by_quantiles(ds, [:L_n_cross, :j0_k, :j0_k_norm])
    df = compute_params!(dropmissing(df))
    spec = data(df) * mapping(; color)
    fs = map([maps1]) do m
        plot_dist(spec, m;
            datalimits=datalimits_f,
            axis,
            figure
        )
    end
    resize_to_layout!.(fs)
    # easy_save.(fnames, fs)
    display.(fs)
end
easy_save("juno_distribution_r_sw")
```
